\documentclass[11pt,a4paper]{article}
\usepackage[margin=1.8cm]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{longtable}
\title{RPG Guild At-Will Main Character LongLive Story Summary}
\author{Agora Mini Interaction Runner}
\date{\today}
\begin{document}
\maketitle
\tableofcontents

\section{Run Overview}
\textbf{Run Dir}: \url{/home/yz\_wang/yz\_main/agora-mini/output/guild\_interaction\_simulation\_atwill\_mainchars/20260422\_224015\_995854}\\
\textbf{World}: RPG Guild Main Character At-Will LongLive Test\\
\textbf{Objective}: Run 103 agents for 25 rounds at activation 0.15. The three protagonists activate every round and each protagonist activity must open LongLive; other activated agents may also use freeform at-will LongLive, with a 10-video-per-round cap. No predefined video task routes are available.\\
\textbf{Target Legality Failures}: 0\\

\section{Route Mix}
\begin{longtable}{lr}
\textbf{Route} & \textbf{Count}\\
model\_cinematic\_interaction & 145 \\
coordinate\_party & 82 \\
trade\_supplies & 79 \\
inspect\_quest\_map & 34 \\
research\_spellwork & 28 \\
repair\_gear & 21 \\
mediate\_party\_dispute & 15 \\
celebrate\_clearance & 8 \\
train\_sparring\_notes & 8 \\
chat\_at\_guild & 6 \\
scout\_report & 6 \\
cook\_rations & 5 \\
heal\_after\_training & 4 \\
buff\_for\_commission & 3 \\
\end{longtable}

\section{LongLive Status}
\begin{longtable}{lr}
\textbf{Status} & \textbf{Count}\\
ok & 77 \\
failed & 68 \\
\end{longtable}

\section{Image Artifact Status}
\begin{longtable}{lr}
\textbf{Status} & \textbf{Count}\\
none & 0 \\
\end{longtable}

\section{API Story Summary}
Over 25 rounds, the guild managed goblin raids, missing caravans, and beast strikes while decoding a royal relic leading to deep ruins. The economy relied heavily on supply trades and gear repairs to deploy teams. Protagonists used cinematic LongLive interactions to coordinate missions and research artifacts.

\subsection{Quest and Trade}
High quest momentum driven by sequential discoveries and urgent threats. Robust economy with 79 supply trades and 21 gear repairs resolving bottlenecks.

\subsection{Video Prompt Chain}
Prompts focused on cooperative tasks like map reading and magical stabilization, using a 0-10 second split to transition from setup to collaborative resolution.

\subsection{Image Artifacts}
No image artifacts generated.

\section{Round-by-Round Story}
\subsection{API Round 1}
Goblin raid posted and artifact discovered. Members traded supplies and formed strike teams.
\newline \textbf{Trade or task thread}: coordinate\_party
\newline \textbf{Representative interaction}: Ren and Eri aligned tactics for the goblin raid.

\subsection{API Round 6}
Vault scout returned and caravan went missing. Warehouse gravity anomaly handled via cinematic interactions.
\newline \textbf{Trade or task thread}: model\_cinematic\_interaction
\newline \textbf{Representative interaction}: Sora and Sora stabilized floating warehouse crates.

\subsection{API Round 14}
Beast lair strike requested. Heavy coordination to deploy arcane backup and repair gear.
\newline \textbf{Trade or task thread}: coordinate\_party
\newline \textbf{Representative interaction}: Renji and Mika organized the beast lair strike team.

\subsection{API Round 25}
Beast core weapon assigned and ruins shortcut verified. Final expedition preparations concluded.
\newline \textbf{Trade or task thread}: coordinate\_party
\newline \textbf{Representative interaction}: Guild cadre finalized weapon assignments for the deep ruins.

\subsection{Round 1}
Activated agents: 17; intents: 18; video jobs: 3; image jobs: 0; action successes: 18.

Ren Ashbell coordinated with Ren Moonvale in tavern\_corner. Kiri Ashbell reviewed sparring notes with Kiri Ironleaf in training\_yard. Emi Serene coordinated with Haru Silverbrook in dormitory. Eri Moonvale coordinated with Eri Silverbrook in strategy\_table. Ren Starling traded supplies with Ren Oakspire in tavern\_corner as part of the supply economy. Toma Starling healed Toma Ashbell in infirmary. Haru Starling coordinated with Kaelen Ironheart in dormitory. Mika Dawncrest coordinated with Mika Ironleaf in quest\_board. 9 additional interactions continued in the background.

\subsection{Round 2}
Activated agents: 18; intents: 19; video jobs: 3; image jobs: 0; action successes: 19.

Eri Moonvale coordinated with Eri Ironleaf in strategy\_table. Ren Ironleaf mediated a party dispute with Ren Ashbell in tavern\_corner. Yuna Starling repaired gear for Elara Vane in forge. Yuna Dawncrest repaired gear for Yuna Starling in forge. Sora Mistfell traded supplies with Sora Dawncrest in warehouse as part of the supply economy. Ari Brightford repaired gear for Ari Emberlane in guild\_hall. Mika Brightford repaired gear for Mika Ashbell in quest\_board. Ren Oakspire mediated a party dispute with Ren Moonvale in tavern\_corner. 10 additional interactions continued in the background.

\subsection{Round 3}
Activated agents: 18; intents: 21; video jobs: 5; image jobs: 0; action successes: 21.

Mika Ashbell checked a quest map with Mika Silverbrook in quest\_board. Ari Moonvale prepared Ari Silverbrook in guild\_hall. Ren Moonvale mediated a party dispute with Ren Dawncrest in tavern\_corner. Kiri Moonvale traded supplies with Kiri Brightford in training\_yard as part of the supply economy. Eri Moonvale performed a freeform LongLive interaction with Eri Ashbell in strategy\_table in a cinematic body-cooperation action (ok). Ari Ironleaf prepared Mira Ledgerfall in guild\_hall. Eri Starling researched spellwork with Eri Dawncrest in strategy\_table. Yuna Dawncrest repaired gear for Yuna Moonvale in forge. 10 additional interactions continued in the background.

\subsection{Round 4}
Activated agents: 15; intents: 16; video jobs: 4; image jobs: 0; action successes: 16.

Eri Ironleaf checked a quest map with Eri Starling in strategy\_table. Haru Starling researched spellwork with Haru Oakspire in dormitory. Ari Dawncrest celebrated a quest clearance with Ari Moonvale in guild\_hall. Ari Mistfell coordinated with Ari Brightford in guild\_hall. Toma Mistfell repaired gear for Toma Ashbell in infirmary. Haru Mistfell performed a freeform LongLive interaction with Haru Starling in dormitory in a cinematic body-cooperation action (ok). Natsu Brightford researched spellwork with Natsu Oakspire 078 in arcane\_library. Eri Brightford checked a quest map with Eri Emberlane in strategy\_table. 7 additional interactions continued in the background.

\subsection{Round 5}
Activated agents: 15; intents: 20; video jobs: 4; image jobs: 0; action successes: 20.

Kaelen Vane traded supplies with Ari Oakspire in guild\_hall as part of the supply economy. Toma Moonvale coordinated with Toma Dawncrest in infirmary. Yuna Ironleaf traded supplies with Elara Vane in forge as part of the supply economy. Natsu Ironleaf researched spellwork with Natsu Dawncrest in arcane\_library. Ari Dawncrest performed a freeform LongLive interaction with Kaelen Vane in guild\_hall in a cinematic body-cooperation action (ok). Sora Dawncrest traded supplies with Sora Brightford in warehouse as part of the supply economy. Mika Brightford spoke with Mika Moonvale in quest\_board. Ren Brightford traded supplies with Ren Silverbrook in tavern\_corner as part of the supply economy. 7 additional interactions continued in the background.

\subsection{Round 6}
Activated agents: 18; intents: 20; video jobs: 10; image jobs: 0; action successes: 20.

Mika Ashbell repaired gear for Mika Mistfell in quest\_board. Ren Ashbell performed a freeform LongLive interaction with Ren Brightford in tavern\_corner in a cinematic body-cooperation action (ok). Yuna Moonvale traded supplies with Yuna Brightford in forge as part of the supply economy. Eri Moonvale delivered a scout report to Eri Silverbrook in strategy\_table. Ari Starling performed a freeform LongLive interaction with Ari Ironleaf in guild\_hall in a cinematic body-cooperation action (ok). Ren Starling mediated a party dispute with Ren Brightford in tavern\_corner. Ren Dawncrest performed a freeform LongLive interaction with Ren Ironleaf in tavern\_corner in a cinematic body-cooperation action (ok). Sora Brightford performed a freeform LongLive interaction with Sora Mistfell in warehouse in a cinematic body-cooperation action (ok). 10 additional interactions continued in the background.

\subsection{Round 7}
Activated agents: 16; intents: 18; video jobs: 6; image jobs: 0; action successes: 18.

Kiri Ashbell reviewed sparring notes with Kiri Starling in training\_yard. Natsu Ashbell researched spellwork with Natsu Oakspire 078 in arcane\_library. Emi Serene performed a freeform LongLive interaction with Haru Mistfell in dormitory in a cinematic body-cooperation action (ok). Mika Ironleaf checked a quest map with Mika Mistfell in quest\_board. Natsu Ironleaf researched spellwork with Natsu Oakspire 078 in arcane\_library. Sora Dawncrest traded supplies with Sora Starling in warehouse as part of the supply economy. Yuna Dawncrest performed a freeform LongLive interaction with Yuna Moonvale in forge in a cinematic body-cooperation action (ok). Ari Mistfell prepared Kaelen Vane in guild\_hall. 8 additional interactions continued in the background.

\subsection{Round 8}
Activated agents: 18; intents: 22; video jobs: 8; image jobs: 0; action successes: 22.

Eri Ashbell performed a freeform LongLive interaction with Eri Starling in strategy\_table in a cinematic body-cooperation action (ok). Yuna Ironleaf celebrated a quest clearance with Yuna Emberlane in forge. Eri Ironleaf traded supplies with Eri Brightford in strategy\_table as part of the supply economy. Haru Starling performed a freeform LongLive interaction with Haru Ironleaf in dormitory in a cinematic body-cooperation action (ok). Ari Dawncrest celebrated a quest clearance with Ari Mistfell in guild\_hall. Toma Dawncrest spoke with Toma Emberlane in infirmary. Ari Mistfell traded supplies with Ari Dawncrest in guild\_hall as part of the supply economy. Sora Mistfell performed a freeform LongLive interaction with Sora Emberlane in warehouse in a cinematic body-cooperation action (ok). 10 additional interactions continued in the background.

\subsection{Round 9}
Activated agents: 18; intents: 20; video jobs: 4; image jobs: 0; action successes: 20.

Eri Ashbell checked a quest map with Eri Emberlane in strategy\_table. Mika Moonvale checked a quest map with Mika Brightford in quest\_board. Toma Moonvale checked a quest map with Toma Emberlane in infirmary. Sora Ironleaf checked a quest map with Sora Moonvale in warehouse. Kiri Starling checked a quest map with Kiri Mistfell in training\_yard. Eri Starling checked a quest map with Eri Ironleaf in strategy\_table. Mika Dawncrest checked a quest map with Mika Emberlane in quest\_board. Yuna Dawncrest traded supplies with Yuna Brightford in forge as part of the supply economy. 10 additional interactions continued in the background.

\subsection{Round 10}
Activated agents: 16; intents: 20; video jobs: 3; image jobs: 0; action successes: 20.

Kaelen Vane traded supplies with Ari Mistfell in guild\_hall as part of the supply economy. Elara Vane traded supplies with Yuna Starling in forge as part of the supply economy. Emi Serene shared warm rations with Haru Mistfell in dormitory. Sora Ironleaf coordinated with Sora Mistfell in warehouse. Kiri Ironleaf healed Kiri Moonvale in training\_yard. Ari Starling coordinated with Ari Mistfell in guild\_hall. Haru Starling shared warm rations with Kaelen Ironheart in dormitory. Kaelen Ironheart shared warm rations with Haru Silverbrook in dormitory. 8 additional interactions continued in the background.

\subsection{Round 11}
Activated agents: 15; intents: 17; video jobs: 6; image jobs: 0; action successes: 17.

Eri Ashbell coordinated with Eri Brightford in strategy\_table. Mika Ironleaf coordinated with Mika Ashbell in quest\_board. Yuna Ironleaf performed a freeform LongLive interaction with Yuna Starling in forge in a cinematic body-cooperation action (ok). Toma Ironleaf coordinated with Toma Moonvale in infirmary. Natsu Ironleaf researched spellwork with Natsu Moonvale in arcane\_library. Eri Ironleaf delivered a scout report to Eri Starling in strategy\_table. Mika Starling performed a freeform LongLive interaction with Mika Emberlane in quest\_board in a cinematic body-cooperation action (ok). Yuna Starling traded supplies with Yuna Brightford in forge as part of the supply economy. 7 additional interactions continued in the background.

\subsection{Round 12}
Activated agents: 12; intents: 17; video jobs: 5; image jobs: 0; action successes: 17.

Elara Vane traded supplies with Yuna Brightford in forge as part of the supply economy. Toma Ashbell coordinated with Toma Silverbrook in infirmary. Natsu Ashbell coordinated with Natsu Moonvale in arcane\_library. Ari Starling traded supplies with Ari Oakspire in guild\_hall as part of the supply economy. Yuna Starling traded supplies with Yuna Oakspire in forge as part of the supply economy. Mika Dawncrest performed a freeform LongLive interaction with Mika Ironleaf in quest\_board in a cinematic body-cooperation action (ok). Haru Mistfell traded supplies with Haru Starling in dormitory as part of the supply economy. Mika Oakspire traded supplies with Mika Moonvale in quest\_board as part of the supply economy. 4 additional interactions continued in the background.

\subsection{Round 13}
Activated agents: 16; intents: 21; video jobs: 5; image jobs: 0; action successes: 21.

Mika Ashbell traded supplies with Mika Brightford in quest\_board as part of the supply economy. Ren Moonvale repaired gear for Ren Mistfell in tavern\_corner. Natsu Moonvale researched spellwork with Natsu Oakspire 078 in arcane\_library. Toma Ironleaf coordinated with Toma Emberlane in infirmary. Ren Starling performed a freeform LongLive interaction with Celestia Vale in tavern\_corner in a cinematic body-cooperation action (ok). Ren Dawncrest repaired gear for Ren Mistfell in tavern\_corner. Sora Dawncrest traded supplies with Kaelen Thorne in warehouse as part of the supply economy. Kaelen Ironheart performed a freeform LongLive interaction with Haru Brightford in dormitory in a cinematic body-cooperation action (ok). 8 additional interactions continued in the background.

\subsection{Round 14}
Activated agents: 22; intents: 24; video jobs: 7; image jobs: 0; action successes: 24.

Mika Ashbell coordinated with Mika Brightford in quest\_board. Ren Ashbell coordinated with Ren Emberlane in tavern\_corner. Elara Vane repaired gear for Yuna Ironleaf in forge. Toma Ashbell coordinated with Toma Moonvale in infirmary. Mika Moonvale coordinated with Mika Dawncrest in quest\_board. Yuna Moonvale traded supplies with Yuna Starling in forge as part of the supply economy. Yuna Ironleaf performed a freeform LongLive interaction with Yuna Emberlane in forge in a cinematic body-cooperation action (ok). Mika Starling coordinated with Mika Ironleaf in quest\_board. 14 additional interactions continued in the background.

\subsection{Round 15}
Activated agents: 20; intents: 22; video jobs: 10; image jobs: 0; action successes: 22.

Kaelen Vane mediated a party dispute with Ari Dawncrest in guild\_hall. Eri Ashbell checked a quest map with Eri Silverbrook in strategy\_table. Yuna Moonvale performed a freeform LongLive interaction with Kaelen Forgeheart in forge in a cinematic body-cooperation action (ok). Kiri Moonvale performed a freeform LongLive interaction with Kiri Starling in training\_yard in a cinematic body-cooperation action (ok). Ari Starling mediated a party dispute with Ari Brightford in guild\_hall. Ren Starling performed a freeform LongLive interaction with Ren Mistfell in tavern\_corner in a cinematic body-cooperation action (ok). Mika Dawncrest performed a freeform LongLive interaction with Mika Ironleaf in quest\_board in a cinematic body-cooperation action (ok). Yuna Dawncrest traded supplies with Yuna Oakspire in forge as part of the supply economy. 12 additional interactions continued in the background.

\subsection{Round 16}
Activated agents: 17; intents: 21; video jobs: 7; image jobs: 0; action successes: 21.

Elara Vane traded supplies with Kaelen Forgeheart in forge as part of the supply economy. Toma Moonvale coordinated with Toma Silverbrook in infirmary. Ari Ironleaf mediated a party dispute with Mira Ledgerfall in guild\_hall. Sora Ironleaf traded supplies with Sora Brightford in warehouse as part of the supply economy. Haru Ironleaf spoke with Haru Starling in dormitory. Ren Starling performed a freeform LongLive interaction with Ren Mistfell in tavern\_corner in a cinematic body-cooperation action (failed). Mika Dawncrest coordinated with Mika Starling in quest\_board. Mika Mistfell performed a freeform LongLive interaction with Mika Emberlane in quest\_board in a cinematic body-cooperation action (failed). 9 additional interactions continued in the background.

\subsection{Round 17}
Activated agents: 23; intents: 27; video jobs: 9; image jobs: 0; action successes: 27.

Ren Ashbell performed a freeform LongLive interaction with Ren Emberlane in tavern\_corner in a cinematic body-cooperation action (failed). Ren Moonvale performed a freeform LongLive interaction with Ren Ashbell in tavern\_corner in a cinematic body-cooperation action (failed). Kiri Moonvale reviewed sparring notes with Kiri Ironleaf in training\_yard. Elara Vane performed a freeform LongLive interaction with Haru Silverbrook in dormitory in a cinematic body-cooperation action (failed). Sora Ironleaf traded supplies with Sora Mistfell in warehouse as part of the supply economy. Yuna Ironleaf repaired gear for Renjiro, Guild Coordinator in forge. Natsu Ironleaf researched spellwork with Natsu Ashbell in arcane\_library. Haru Ironleaf healed Kaelen Ironheart in dormitory. 15 additional interactions continued in the background.

\subsection{Round 18}
Activated agents: 16; intents: 16; video jobs: 10; image jobs: 0; action successes: 16.

Natsu Ashbell performed a freeform LongLive interaction with Natsu Ironleaf in arcane\_library in a cinematic body-cooperation action (failed). Eri Moonvale coordinated with Eri Ashbell in strategy\_table. Toma Ironleaf performed a freeform LongLive interaction with Toma Starling in infirmary in a cinematic body-cooperation action (failed). Kiri Ironleaf repaired gear for Kiri Mistfell in training\_yard. Mika Dawncrest coordinated with Mika Mistfell in quest\_board. Toma Mistfell performed a freeform LongLive interaction with Toma Silverbrook in infirmary in a cinematic body-cooperation action (failed). Kiri Mistfell repaired gear for Kiri Silverbrook in training\_yard. Ari Brightford coordinated with Ari Starling in guild\_hall. 8 additional interactions continued in the background.

\subsection{Round 19}
Activated agents: 20; intents: 21; video jobs: 4; image jobs: 0; action successes: 21.

Mika Ashbell coordinated with Mika Dawncrest in quest\_board. Ren Ashbell checked a quest map with Celestia Vale in tavern\_corner. Sora Ashbell coordinated with Sora Dawncrest in warehouse. Natsu Moonvale researched spellwork with Natsu Ironleaf in arcane\_library. Sora Ironleaf traded supplies with Sora Dawncrest in warehouse as part of the supply economy. Haru Ironleaf coordinated with Kaelen Ironheart in dormitory. Ren Starling coordinated with Ren Brightford in tavern\_corner. Yuna Starling coordinated with Yuna Ironleaf in forge. 12 additional interactions continued in the background.

\subsection{Round 20}
Activated agents: 19; intents: 25; video jobs: 3; image jobs: 0; action successes: 25.

Sora Ashbell traded supplies with Sora Moonvale in warehouse as part of the supply economy. Emi Serene researched spellwork with Haru Starling in dormitory. Eri Moonvale coordinated with Eri Emberlane in strategy\_table. Ari Ironleaf checked a quest map with Ari Silverbrook in guild\_hall. Ren Ironleaf traded supplies with Ren Brightford in tavern\_corner as part of the supply economy. Eri Ironleaf traded supplies with Eri Mistfell in strategy\_table as part of the supply economy. Sora Dawncrest traded supplies with Sora Ashbell in warehouse as part of the supply economy. Eri Dawncrest coordinated with Eri Emberlane in strategy\_table. 11 additional interactions continued in the background.

\subsection{Round 21}
Activated agents: 21; intents: 27; video jobs: 6; image jobs: 0; action successes: 27.

Sora Ashbell traded supplies with Sora Ironleaf in warehouse as part of the supply economy. Elara Vane traded supplies with Kaelen Forgeheart in forge as part of the supply economy. Toma Ashbell performed a freeform LongLive interaction with Toma Dawncrest in infirmary in a cinematic body-cooperation action (failed). Natsu Ashbell researched spellwork with Natsu Oakspire 078 in arcane\_library. Toma Moonvale traded supplies with Toma Mistfell in infirmary as part of the supply economy. Elara Vane mediated a party dispute with Haru Silverbrook in dormitory. Mika Starling traded supplies with Mika Oakspire in quest\_board as part of the supply economy. Toma Starling performed a freeform LongLive interaction with Toma Ashbell in infirmary in a cinematic body-cooperation action (failed). 13 additional interactions continued in the background.

\subsection{Round 22}
Activated agents: 21; intents: 23; video jobs: 10; image jobs: 0; action successes: 23.

Mika Ashbell performed a freeform LongLive interaction with Mika Oakspire in quest\_board in a cinematic body-cooperation action (failed). Ari Moonvale performed a freeform LongLive interaction with Mira Ledgerfall in guild\_hall in a cinematic body-cooperation action (failed). Mika Starling checked a quest map with Mika Dawncrest in quest\_board. Eri Starling researched spellwork with Eri Dawncrest in strategy\_table. Eri Dawncrest performed a freeform LongLive interaction with Eri Ashbell in strategy\_table in a cinematic body-cooperation action (failed). Ari Mistfell performed a freeform LongLive interaction with Ari Starling in guild\_hall in a cinematic body-cooperation action (failed). Kaelen Forgeheart performed a freeform LongLive interaction with Yuna Dawncrest in forge in a cinematic body-cooperation action (failed). Natsu Mistfell researched spellwork with Natsu Starling in arcane\_library. 13 additional interactions continued in the background.

\subsection{Round 23}
Activated agents: 21; intents: 27; video jobs: 7; image jobs: 0; action successes: 27.

Sora Ashbell traded supplies with Sora Ironleaf in warehouse as part of the supply economy. Elara Vane coordinated with Yuna Moonvale in forge. Kiri Ashbell reviewed sparring notes with Kiri Dawncrest in training\_yard. Sora Moonvale traded supplies with Sora Mistfell in warehouse as part of the supply economy. Yuna Moonvale performed a freeform LongLive interaction with Yuna Ironleaf in forge in a cinematic body-cooperation action (failed). Eri Moonvale performed a freeform LongLive interaction with Eri Oakspire in strategy\_table in a cinematic body-cooperation action (failed). Mika Ironleaf coordinated with Mika Dawncrest in quest\_board. Eri Starling checked a quest map with Eri Silverbrook in strategy\_table. 13 additional interactions continued in the background.

\subsection{Round 24}
Activated agents: 19; intents: 25; video jobs: 3; image jobs: 0; action successes: 25.

Sora Ashbell traded supplies with Sora Starling in warehouse as part of the supply economy. Emi Serene coordinated with Haru Oakspire in dormitory. Sora Moonvale traded supplies with Sora Brightford in warehouse as part of the supply economy. Sora Ironleaf traded supplies with Sora Emberlane in warehouse as part of the supply economy. Ren Dawncrest checked a quest map with Ren Ironleaf in tavern\_corner. Natsu Dawncrest checked a quest map with Natsu Mistfell in arcane\_library. Kaelen Ironheart mediated a party dispute with Haru Emberlane in dormitory. Yuna Brightford traded supplies with Yuna Moonvale in forge as part of the supply economy. 11 additional interactions continued in the background.

\subsection{Round 25}
Activated agents: 13; intents: 15; video jobs: 3; image jobs: 0; action successes: 15.

Ari Ironleaf coordinated with Ari Silverbrook in guild\_hall. Ari Dawncrest coordinated with Ari Moonvale in guild\_hall. Ren Mistfell spoke with Ren Brightford in tavern\_corner. Kiri Mistfell repaired gear for Kiri Ashbell in training\_yard. Eri Mistfell coordinated with Eri Starling in strategy\_table. Mika Oakspire traded supplies with Mika Mistfell in quest\_board as part of the supply economy. Haru Oakspire checked a quest map with Haru Brightford in dormitory. Kiri Emberlane coordinated with Kiri Ashbell in training\_yard. 5 additional interactions continued in the background.

\section{Representative Video Prompts}
\begin{enumerate}
\item \textbf{guild\_main\_cadre -> guild\_081} status=ok\\\newline Actor prompt: Japanese fantasy RPG guild hall, bustling atmosphere. Mira Ledgerfall, an androgynous senior cadre in a navy cloak with gold trim and silver hair, stands at a polished wooden table holding a leather-bound ledger. She points to a detailed quest map spread across the table. Ari Emberlane, a feminine scout in a cropped travel jacket and messenger straps, leans in beside her, both characters focused on the map. Cinematic lighting, high-quality anime aesthetic, no text, no watermark.\\\newline Target continuation: Same continuous Japanese fantasy guild shot. Ari Emberlane nods in agreement, reaching out to help Mira Ledgerfall align the map edges. Together, they place a heavy brass guild seal onto a commission document on the table. Mira offers a brief, confident nod of approval as Ari adjusts her messenger straps, both characters maintaining consistent appearances and fluid, professional body cooperation. No text, no watermark.\\\newline Config: \url{/home/yz\_wang/yz\_main/agora-mini/output/guild\_interaction\_simulation\_atwill\_mainchars/20260422\_224015\_995854/longlive\_jobs/r001\_0015\_guild\_main\_cadre\_guild\_081/configs/longlive\_config.yaml}\\\newline Video: \url{/home/yz\_wang/yz\_main/agora-mini/output/guild\_interaction\_simulation\_atwill\_mainchars/20260422\_224015\_995854/longlive\_jobs/r001\_0015\_guild\_main\_cadre\_guild\_081/videos/cinematic\_interaction.mp4}
\item \textbf{guild\_main\_hero -> guild\_022} status=ok\\\newline Actor prompt: Japanese fantasy RPG guild scene, Renji Dawnblade in a crimson guild cloak and Mika Ironleaf in a green half-cape; Renji spreads a weathered quest map across a wooden table, pointing to a marked location while looking at Mika, who leans in with an alert expression, cinematic lighting, anime aesthetic, no text, no watermark.\\\newline Target continuation: Same continuous Japanese fantasy guild shot; after ten seconds Mika Ironleaf nods, placing her finger on the map to trace a path, while Renji Dawnblade smiles and nods in agreement, both characters fully engaged in planning the quest, consistent identities and camera, no text, no watermark.\\\newline Config: \url{/home/yz\_wang/yz\_main/agora-mini/output/guild\_interaction\_simulation\_atwill\_mainchars/20260422\_224015\_995854/longlive\_jobs/r001\_0016\_guild\_main\_hero\_guild\_022/configs/longlive\_config.yaml}\\\newline Video: \url{/home/yz\_wang/yz\_main/agora-mini/output/guild\_interaction\_simulation\_atwill\_mainchars/20260422\_224015\_995854/longlive\_jobs/r001\_0016\_guild\_main\_hero\_guild\_022/videos/cinematic\_interaction.mp4}
\item \textbf{guild\_main\_princess -> guild\_053} status=ok\\\newline Actor prompt: Japanese fantasy RPG guild scene, Celestia Vale in a modest travel dress and Ren Mistfell in a tool-belt apron; Celestia points to glowing magical residue spilled from a crate on a workbench, Ren gestures for caution and begins pulling on protective leather gloves, warm tavern lighting, anime style, no text, no watermark.\\\newline Target continuation: Same continuous Japanese fantasy guild shot; after ten seconds Ren uses long iron tongs to carefully lift a shimmering crystal shard from the residue, placing it into a lead-lined box while Celestia watches with focused interest, consistent characters and camera, no text, no watermark.\\\newline Config: \url{/home/yz\_wang/yz\_main/agora-mini/output/guild\_interaction\_simulation\_atwill\_mainchars/20260422\_224015\_995854/longlive\_jobs/r001\_0017\_guild\_main\_princess\_guild\_053/configs/longlive\_config.yaml}\\\newline Video: \url{/home/yz\_wang/yz\_main/agora-mini/output/guild\_interaction\_simulation\_atwill\_mainchars/20260422\_224015\_995854/longlive\_jobs/r001\_0017\_guild\_main\_princess\_guild\_053/videos/cinematic\_interaction.mp4}
\item \textbf{guild\_main\_hero -> guild\_082} status=ok\\\newline Actor prompt: Japanese fantasy RPG guild scene, Renji Dawnblade in a crimson guild cloak and Mika Emberlane in a cropped travel jacket standing at a wooden quest table; Renji unfolds a weathered, detailed quest map and gestures for Mika to examine a specific region, clear body action of collaborative planning, cinematic lighting, vibrant anime aesthetic, no text, no watermark.\\\newline Target continuation: Same continuous Japanese fantasy guild shot; Mika Emberlane leans in to trace a strategic route on the map with a finger, looking up at Renji Dawnblade with a determined nod, Renji responds by firmly placing his hand on the table to finalize the plan, consistent identities and camera, no text, no watermark.\\\newline Config: \url{/home/yz\_wang/yz\_main/agora-mini/output/guild\_interaction\_simulation\_atwill\_mainchars/20260422\_224015\_995854/longlive\_jobs/r002\_0016\_guild\_main\_hero\_guild\_082/configs/longlive\_config.yaml}\\\newline Video: \url{/home/yz\_wang/yz\_main/agora-mini/output/guild\_interaction\_simulation\_atwill\_mainchars/20260422\_224015\_995854/longlive\_jobs/r002\_0016\_guild\_main\_hero\_guild\_082/videos/cinematic\_interaction.mp4}
\item \textbf{guild\_main\_princess -> guild\_093} status=ok\\\newline Actor prompt: Japanese fantasy RPG guild scene, Celestia Vale in a travel dress and Ren Silverbrook in a formal cloak; Celestia spreads a large, weathered quest map across the wooden guild counter, looking toward Ren for guidance. Warm tavern lighting, cinematic medium shot, anime style, no text, no watermark.\\\newline Target continuation: Same continuous Japanese fantasy guild shot; Ren Silverbrook leans in and places his heavy brass guild seal firmly onto the corner of the map to hold it flat, while Celestia Vale traces a route on the parchment with her finger, both nodding in mutual agreement. Consistent tavern background, anime art style, no text, no watermark.\\\newline Config: \url{/home/yz\_wang/yz\_main/agora-mini/output/guild\_interaction\_simulation\_atwill\_mainchars/20260422\_224015\_995854/longlive\_jobs/r002\_0017\_guild\_main\_princess\_guild\_093/configs/longlive\_config.yaml}\\\newline Video: \url{/home/yz\_wang/yz\_main/agora-mini/output/guild\_interaction\_simulation\_atwill\_mainchars/20260422\_224015\_995854/longlive\_jobs/r002\_0017\_guild\_main\_princess\_guild\_093/videos/cinematic\_interaction.mp4}
\end{enumerate}

\section{Representative Image Artifacts}
\begin{enumerate}
\item No still-image artifact jobs were recorded.
\end{enumerate}

\section{Artifacts}
Story JSON: \url{/home/yz\_wang/yz\_main/agora-mini/output/guild\_interaction\_simulation\_atwill\_mainchars/20260422\_224015\_995854/guild\_atwill\_mainchars\_story.json}\\
Timeline JSONL: \url{/home/yz\_wang/yz\_main/agora-mini/output/guild\_interaction\_simulation\_atwill\_mainchars/20260422\_224015\_995854/timeline.jsonl}\\
Video Jobs JSONL: \url{/home/yz\_wang/yz\_main/agora-mini/output/guild\_interaction\_simulation\_atwill\_mainchars/20260422\_224015\_995854/video\_prompt\_jobs.jsonl}\\
Image Jobs JSONL: \url{/home/yz\_wang/yz\_main/agora-mini/output/guild\_interaction\_simulation\_atwill\_mainchars/20260422\_224015\_995854/image\_jobs.jsonl}\\
\end{document}
